\newpage
\chapter{Conclusion}
\mbox{}\vspace{-\baselineskip}

Peculiar features of missing mass distributions were investigated by close examination of the quantities $M^{2}_{X[\pi^{-}]}$ and $M^{2}_{X[0]}$ for the double-pion electroproduction off protons. The five factors, which typically affect the missing mass distributions in experimental studies of exclusive reactions, were examined in detail, i.e. radiative effects, admixtures from other channels, detector resolution, Fermi smearing, and final state interactions with spectator nucleons. The influence of each factor was investigated individually. The examination is supported by the theoretical calculations and the Monte-Carlo simulation.

\everypar{\looseness=-1}
Various combinations of the considered five factors are thought to cover the vast majority of the situations that can be observed in experiments of meson photo- and electroproduction off protons (including both cases of free and bound protons and different beam energies). This examination is therefore intended to facilitate the challenging task of isolating a particular reaction channel during the data analysis process and hence may be helpful for future CLAS12 experiments.


Beyond that, the modeling of kinematic manifestations of final state interactions with spectator nucleons is attempted in Sect.~\ref{sec:fsi}. This modeling may be of special interest for studies of exclusive reactions off bound nucleons as it represents a step towards the reliable simulation of these complicated and so far not fully explored effects.

If needed for comparison, experimental distributions of the considered missing quantities can be found e.g. in Refs.~\cite{Fed_an_note:2017,Fed_paper_2018,Arjun} for the double-pion electroproduction off free protons and in Refs.~\cite{Skorodumina:2015rea,skorodum_an_note:2019} for the reaction occurring off protons bound in deuterium.


